A Handbook for Tenured Track Faculty in Computer Science in the US

### 2024-08-15 faculty.tex
updates

\chapter{Research}\label{chap:research}
This section focuses on paper publication, which is a major component of P\&T and of course in getting your name out there. P\&T evaluation requires no specific conferences/journals or numbers of papers, but typically you will want to have a good number of papers in top venues. P\&T members or letter writers (obviously) are familiar with top places in your field, and they will definitely look for those in your profile.
Work that won awards, e.g., paper awards, can help a lot in tenure evaluation. Papers with very high citations also help.  Research areas that you started and are now popular also count.  Finally, new research directions that can help get grants are also good.

@@

Depending on your research area, you might focus on publishing at top conferences or journals.  You probably should know what's popular in your area already (if not, ask your senior colleagues). If you're at an R1 university, you will want to publish at top venues, and not just any venue.  You should also aim to publish at a variety of venues, and not just one.  This will show that your research is of interest to a wide range of people.

\paragraph{Conferences}
In most CS fields, top conferences are more common and competitive than journals. Each field also has several of such top conferences yearly (e.g., in Software Engineering, ICSE, FSE, ASE, and ISSTA are top four).  They are often scheduled so that if you miss (or get rejected) from one, you can submit to another.

@@

\paragraph{Artifact Evaluation}

\paragraph{Journals}
In some journals are more common and prestigious. Moreover, many areas have top journals in additions to well-known conferences (e.g., Trans. of Software Engr. or TSE is a very well-known journal in Software Engineering, which has 4 major confs.).  Typically, or at least in SE, the common approach is publishing new work to conference and followup work to journals (e.g., so the journal paper is an substantial extension of the conf. paper with new experiments, studies, theorems, etc). In some sense, journals are for more mature work, and conferences are for new ideas.

\paragraph{Short papers, workshops, etc}

\section{Collaboration and co-authorship}
While it's general true that profs. are busy, but for me and probably many others, it's not the main reason.  I do skim every single emails from prospective students, but I ignore most of them because they were quite generic (likely written for dozen of other profs.).  Sometimes they try to "customize" it by mentioning the names of my papers, but

.  So even if I am not busy (e.g., spending time on reddit), I still would not reply to such emails.

\paragraph{Papers with your adviser(s)}

>>>>

\chapter{Research and Publications}\label{chap:research}

This section focuses on research publication, which is a major component of P\&T and of course in getting your name out there. P\&T evaluation requires no specific conferences/journals or numbers of papers, but typically you will want to have a good number of papers in top venues.
%P\&T members or letter writers (obviously) are familiar with top places in your field, and they will definitely look for those in your profile.
Work that won awards, e.g., best paper awards, can help a lot in P\&T. Papers with very high citations also help.  Research areas that you started and are now popular also count.  Finally, new research directions that can help get grants are also good.

@@

Depending on your research area, you might focus on publishing at top conferences or journal.  You probably should know what's popular in your area already (if not, ask your senior colleagues). If you're at an R1 university, you will want to publish at top venues, and not just any venue.  You should also aim to publish at a variety of venues, and not just one.  This will show that your research is of interest to a wide range of people.

\subsection{Conferences}
In most CS fields, conferences are more common and competitive than journals. Each field has several of top conferences every year (e.g., in Software Engineering, ICSE, FSE, ASE, and ISSTA are top four).  They are often scheduled so that if you miss (or get rejected) from one, you can submit to another.

@@

\paragraph{Artifact Evaluation} This is probably more well-known in SE conferences, and is intended to promote the reproducibility of research results. However, I never liked it because it's a lot of work and many of my experiments require heavy computation that the reviewers do not have.  I also don't think it's very useful as I have always make my code, benchmarks, and results open source (through Github). I found it strange that many SE conference have recently required this as part of the submission process. It makes the submission process much more complicated and much more time-consuming.

\subsection{Journals}
In some fields, journals are more common and prestigious. Moreover, many areas have top journals in additions to well-known conferences (e.g., in addition to the main fource confs as mentioned above, SE also has Trans. of Software Engr. or TSE, which is a very well-known and high-quality journal).  Typically, or at least in SE, the common approach is publishing new work to conference and followup work to journals (e.g., so the journal paper is an substantial extension of the conf. paper with new experiments, studies, theorems, etc). In some sense, journals are for more mature work, and conferences are for new ideas.

While you are not expected to publish regularly in journals, having a few papers in top journals by your tenure evaluation shows the diversity of your research and that you can publish in different venues.

\subsection{Short papers, workshops, etc} Short papers in workshop or non-research tracks at a conference (e.g., tool, demo, vision, etc) do not count as much.
They describe work that might not be as mature (e.g., new idea) or as complete (e.g., a tool or a demo) as a full paper, and also have higher acceptance rate. Many people use them as a way to get feedback on their work before submitting to a full paper venue.  Most new professors do not focus on these kinds of papers. Many P\&T committees do not count or care much about these and having too many of them can be a negative signal.

Personally, I find that such papers are very useful as preliminary work for writing grant proposals. They show that you have a new idea and good preliminary results that are worth pursuing further. Sometimes a full paper is not as good because the research is relatively complete with strong results, which bring the concern that you already did all the cool work and the proposal is minor and not exciting.

\section{FAQs}

\subsection{Your university does not recognize conference value} For most non-CS engineering fields journal are more prestigious than conferences. Places with a strong CS department are well aware of the value of top confs., but many other places are not (especially smaller universities or CS depts run by engineering people). These places also do not know much about the quality of the venue, and so in many cases put a workshop paper in the same class as a top conference paper and also cannot differentiate between a good vs bad journals in CS (because they do not know CS well). Also,  they often value quantity over quality because they cannot properly evaluate paper quality.

This is a cultural issue and is very difficult to change. Many good researchers have left such places because of this.  However, some were able to leverage this and publish at easy places and do really well within their department.  However, while they thrive at such places, they will likely not get funding and recognition in their field.  This is a trade-off that you need to consider.

\subsection{Papers with your adviser(s)}
One common question is whether you should publish papers with your adviser(s) after you start your own lab and become a professor.  The straight answer is that if you collaborate too much with your adviser(s), it's not good and brings concern about you not being an independent researcher (you are already a professor and so are expected to be able to do research on your own). I have seen many cases where a new professor has published many papers with their adviser(s) and then had trouble getting tenure (even renewal).

However, this does not mean you should not work with your adviser(s). You can absolutely continue do research and write grant proposals with them, but you should also work and write papers with other people, and especially your students.
